Creating the ``r params$package_name`` R package

### 2025-10-08 create-FSHybridPLS.Rmd
split and normalize reinvented

## sample splitting

@@

```{r}
#'Split Functional, Scalar, and Response Data
#' @param data_fun_1 fd object (fda package). Functional predictor 1.
#' @param data_fun_2 fd object (fda package). Functional predictor 2.
#' @param data_scalar Matrix. Scalar predictors.
#' @param response Vector. Response variable.
#' @param train_idx Vector. Indices for train data.
#' @return List containing split train and test sets.
#' @export
split.all <- function(data_fun_1, data_fun_2, data_scalar, response, train_idx) {
  # --- Type Checks ---
  stopifnot(
    # Functional data checks (assuming 'fd' class from the 'fda' package)
    inherits(data_fun_1, "fd"),
    inherits(data_fun_2, "fd"),

    # Scalar predictor check
    is.matrix(data_scalar),

    # Response variable check
    is.vector(response) || is.numeric(response) || is.factor(response),

    # Training index check
    is.vector(train_idx),
    is.numeric(train_idx),
    all(train_idx > 0), # Indices should be positive
    all(train_idx == round(train_idx)) # Indices should be integers
  )
  # -------------------

  return(list(
    data_fun_1_train = data_fun_1[train_idx],
    data_fun_1_test = data_fun_1[-train_idx],
    data_fun_2_train = data_fun_2[train_idx],
    data_fun_2_test = data_fun_2[-train_idx],
    data_scalar_train = data_scalar[train_idx, , drop = FALSE],
    data_scalar_test = data_scalar[-train_idx, , drop = FALSE],
    response_train = response[train_idx],
    response_test = response[-train_idx]
  ))
}
```

```{r}
#' 
#' @export
normailize.all <- function(split.all_obj){
  curve_normalize_result_1 <- curve_normalize_train_test_fd(
    split.all_obj$data_fun_1_train,
    split.all_obj$data_fun_1_test)
  data_fun_1_train <- curve_normalize_result_1$train
  data_fun_1_test <- curve_normalize_result_1$test

  curve_normalize_result_2 <- curve_normalize_train_test_fd(
    split.all_obj$data_fun_2_train,
    split.all_obj$data_fun_2_test)
  data_fun_2_train <- curve_normalize_result_2$train
  data_fun_2_test <- curve_normalize_result_2$test

  scalar_normalize_result <- scalar_normalize_train_test(
    split.all_obj$data_scalar_train,
    split.all_obj$data_scalar_test)
  data_scalar_train <- scalar_normalize_result$train
  data_scalar_test <- scalar_normalize_result$test

  between_normalize_result <- btwn_normalize_train_test(
    list(data_fun_1_train, data_fun_2_train),
    data_scalar_train,
    data_scalar_test
  )
  data_scalar_train <- between_normalize_result$train
  data_scalar_test <- between_normalize_result$test

  response_mean_train <-  mean(split.all_obj$response_train)
  response_train <- split.all_obj$response_train - response_mean_train
  response_test <- split.all_obj$response_test - response_mean_train

  return(
    list(
      data_fun_1_train = data_fun_1_train,
      data_fun_2_train = data_fun_2_train,
      data_scalar_train= data_scalar_train,
      response_train   = response_train,
      data_fun_1_test  = data_fun_1_test,
      data_fun_2_test  = data_fun_2_test,
      data_scalar_test = data_scalar_test,
      response_test    = response_test
    )
  )
}
```

@@

```{r}
#' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
#' @param train A `predictor_hybrid` object representing the training set.
#' @param test A `predictor_hybrid` object representing the testing set.
#' @return A list containing:
#'   \item{train}{The normalized training `predictor_hybrid` object.}
#'   \item{test}{The normalized testing `predictor_hybrid` object.}
#'   \item{deno_train}{A numeric vector of scaling factors used for each functional predictor.}
#' @export
curve_normalize_train_test <- function(train, test) {
  # --- Type Checks ---
  stopifnot(
    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid"),
    "Mismatch in number of functional predictors" = train$n_functional == test$n_functional
  )

  train_normalized <- train
  test_normalized <- test
  deno_train <- numeric(train$n_functional)

  # Iterate through each functional predictor (k)
  for (k in seq_len(train$n_functional)) {

    # 1. Determine centering and scaling factors from the TRAINING data only
    train_fd <- train$functional_list[[k]]

    # Calculate the mean function for centering
    mean_train <- fda::mean.fd(train_fd)

@@

    # 2. Normalize the TRAINING set
    train_normalized$functional_list[[k]] <- curve_normalize(
      train_fd, # Use original train data
      mean_train,
      deno_train[k]
    )

    # 3. Normalize the TEST set (using train factors to prevent leakage)
    test_normalized$functional_list[[k]] <-
      curve_normalize(
        test$functional_list[[k]], # Use original test data
        mean_train, # Centered by training mean
        deno_train[k] # Scaled by training SD
      )
  }

  # Return the modified hybrid objects and the scaling factors
  return( list(
    train = train_normalized,
    test = test_normalized,
    deno_train = deno_train
  ))
}

@@

  return(
    list(
      train = predictor_train_normalized,
      test = predictor_test_normalized
    )
  )
}
```

@@

  return(
    list(
      train = train_normalized,
      test = test_normalized
    )
  )
}

@@

### DataSplitterNormalizer
R6 class to split functional and scalar predictors into train and test sets and apply normalization techniques including curve normalization, scalar normalization, and between-functional-scalar normalization.
```{r}
#' @title Dataset Splitting and Normalization
#' @description 
DataSplitterNormalizer <- R6::R6Class(
  "DataSplitterNormalizer",

>>>>

## sample splitting and normalization

@@

```{r}
#' Split Hybrid Predictor and Response Data
#'
#' Splits the hybrid predictor object and the response vector into training and
#' testing sets based on a given training ratio.
#'
#' @param W_hybrid predictor_hybrid object containing all functional and scalar data.
#' @param response Vector. The response variable corresponding to the samples in W_hybrid.
#' @param train_ratio Numeric scalar between 0 and 1 indicating the proportion of data to use for training.
#' @return List containing split train and test sets for all components.
#' @export
split.all <- function(W_hybrid, response, train_ratio) {
  # --- Type and Ratio Checks ---
  stopifnot(
    "'W_hybrid' must be a predictor_hybrid object" = inherits(W_hybrid, "predictor_hybrid"),
    "'response' must be a vector" = is.vector(response),
    "Response length must match hybrid sample size" = length(response) == W_hybrid$n_sample,
    "'train_ratio' must be between 0 and 1" = is.numeric(train_ratio) && train_ratio > 0 && train_ratio < 1
  )

  N <- W_hybrid$n_sample
  N_train <- floor(N * train_ratio)

  # Generate random indices for training set
  # Using 1:N ensures indices are always valid
  train_idx <- sample(1:N, N_train)
  test_idx <- (1:N)[-train_idx]

  W_train <- predictor_hybrid(
    W_hybrid$Z[train_idx, , drop = FALSE],
    list(
      W_hybrid$functional_list[[1]][train_idx],
      W_hybrid$functional_list[[2]][train_idx]
    )
  )

  W_test <- predictor_hybrid(
    W_hybrid$Z[test_idx, , drop = FALSE],
    list(
      data_fun_1_test = W_hybrid$functional_list[[1]][test_idx],
    data_fun_2_test = W_hybrid$functional_list[[2]][test_idx]
    )
  )

  return( 
    list(
    predictor_train = W_train,
    predictor_test = W_test ,
    response_train = response[train_idx],
    response_test = response[test_idx]
  ))
}
```

@@

```{r}
#' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
#' @param train A `predictor_hybrid` object representing the training set.
#' @param test A `predictor_hybrid` object representing the testing set.
#' @return A list containing:
#'   train: The normalized training `predictor_hybrid` object.}
#'   test: The normalized testing `predictor_hybrid` object.}
#'   deno_train: A numeric vector of scaling factors used for each functional predictor.}
#' @export
curve_normalize_train_test <- function(train, test) {
  # --- Type Checks ---
  stopifnot(
    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid"),
    "Mismatch in number of functional predictors" = train$n_functional == test$n_functional
  )

  train_normalized <- train
  test_normalized <- test
  deno_train <- numeric(train$n_functional)
  mean_train <- list()

  # Iterate through each functional predictor (k)
  for (k in seq_len(train$n_functional)) { 
    # 1. Determine centering and scaling factors from the TRAINING data only
    train_fd <- train$functional_list[[k]]

    # Calculate the mean function for centering
    mean_train[[k]] <- fda::mean.fd(train_fd)

@@

    # 2. Normalize the TRAINING set
    train_normalized$functional_list[[k]] <- curve_normalize(
      train_fd, # Use original train data
      mean_train[[k]],
      deno_train[k]
    )

    # 3. Normalize the TEST set (using train factors to prevent leakage)
    test_normalized$functional_list[[k]] <-
      curve_normalize(
        test$functional_list[[k]], # Use original test data
        mean_train[[k]], # Centered by training mean
        deno_train[k] # Scaled by training SD
      )
  }
  # Return the modified hybrid objects and the scaling factors
  return( list(
    predictor_train = train_normalized,
    predictor_test = test_normalized,
    mean_train = mean_train,
    deno_train = deno_train
  ))
}
```

@@

  return(
    list(
      predictor_train = predictor_train_normalized,
      predictor_test = predictor_test_normalized,
      mean_train = mean_train,
      sd_train = sd_train
    )
  )
}
```

@@

  return(
    list(
      predictor_train = train_normalized,
      predictor_test = test_normalized,
      scaling_factor = scaling_factor
    )
  )
}

@@

```{r}
#' 
#' @export
split_and_normailize.all <- function(W_hybrid, response, train_ratio){

# $W_hybrid =  W_hybrid_mock
#$ response

# train_ratio = TRAIN_RATIO

 # split.result <- split.all(W_hybrid, response, train_ratio)

 #     predictor_train = W_train,
 #   predictor_test = W_test ,
 #   response_train = response[train_idx],
 #   response_test = response[test_idx]

 # list(
 #   train = train_normalized,
 #   test = test_normalized,
 #   mean_train = mean_train,
 #   deno_train = deno_train
#  ))

  curve_normalize_result <- curve_normalize_train_test(split.result$predictor_train, split.result$predictor_test)
  scalar_normalize_result <- scalar_normalize_train_test(curve_normalize_result$predictor_train, curve_normalize_result$predictor_test)
  btwn_normalize_result <- btwn_normalize_train_test(
    scalar_normalize_result$predictor_train,
    scalar_normalize_result$predictor_test
  )

  response_mean_train <-  mean(split.result$response_train)
  response_sd_train <-  sd(split.result$response_train)
  response_train <- (split.result$response_train - response_mean_train)/response_sd_train
  response_test <- (split.result$response_test - response_mean_train)/response_sd_train
  response_normalize_result = list(mean_train = response_mean_train, sd_train = response_sd_train)
  return(
    list(
      predictor_train = btwn_normalize_result$predictor_train,
      predictor_test = btwn_normalize_result$predictor_test,
      response_train = response_train,
      response_test = response_test,
      curve_normalize_result = curve_normalize_result,
      scalar_normalize_result = scalar_normalize_result,
      btwn_normalize_result = btwn_normalize_result,
      response_normalize_result = response_normalize_result
    )
  )
}
```

```{r}
N <- 30
response <- c(1:N)
TRAIN_RATIO <- 0.7
create_mock_fd <- function(N_samples, seed) {
  set.seed(seed)
  mock_basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = 5)
  C <- matrix(rnorm(5 * N_samples, mean = 10), nrow = 5)
  fd(C, mock_basis)
}
# 1. Setup Mock Hybrid Input
W_hybrid_mock <- predictor_hybrid(
  Z = matrix(1:(10*N), ncol = 10), # Simple sequential scalar data for verification
  functional_list = list(
    create_mock_fd(N, 1),
    create_mock_fd(N, 2)
  )
)

# 2. Split the data first
split_obj <- split_and_normailize.all(W_hybrid_mock, response, TRAIN_RATIO)

### DataSplitterNormalizer
R6 class to split functional and scalar predictors into train and test sets and apply normalization techniques including curve normalization, scalar normalization, and between-functional-scalar normalization.

```{r}
#'  Dataset Splitting and Normalization
#' @description 
DataSplitterNormalizer <- R6::R6Class(
  "DataSplitterNormalizer",
